Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2023-01-03 sports_analytics.Rmd
goalie-pulling; #43
fix wording; close #47

Early work on expected point values in American football can also be found in @Carroll1988hidden.
In particular, the authors extend @Carter1971operations's work and propose a linear model for expected points in the NFL.
They determine that every extra 25 yards is associated with 2 more points scored on average for a football team.

@@

The situation gets even more interesting when teams modify both their offensive and defensive strategies simultaneously. 
For example, in hockey teams will often pull their goalie when trailing in the final period. 
This strategy severely weakens their defense but strengthens their offense. 
The hope is to score a quick goal to get back in the game, but the risk is falling further behind. 
@beaudoin2010strategies show that NHL coaches do not always employ the optimal strategies. 
@skinner2011scoring develops a general framework for these desperation strategies, which include the onside kick in American football, pulling the infield and/or outfield in baseball, and of course, the fabled Hack-a-Shaq strategy in basketball.

>>>>

Early work on expected point values in American football can also be found in @Carroll1988hidden.
In particular, the authors consider a similar approach to @Carter1971operations and propose a linear model for expected points in the NFL.
They determine that every extra 25 yards is associated with 2 more points scored on average for a football team.

@@

The situation gets even more interesting when teams modify both their offensive and defensive strategies simultaneously. 
For example, in hockey teams will often pull their goalie when trailing in the final period. 
This strategy severely weakens their defense but strengthens their offense. 
The hope is to score a quick goal to get back in the game, but the risk is falling further behind. 
@beaudoin2010strategies show that NHL coaches do not always employ the optimal strategies, usually by waiting too long to pull their goalies. 
@skinner2011scoring develops a general framework for these desperation strategies, which include the onside kick in American football, pulling the infield and/or outfield in baseball, and of course, the fabled Hack-a-Shaq strategy in basketball.
